This chapter aim to provide more formal description of the different phenomenon that were investigated in this thesis. The chapter gives a formal definition of a conversation, turn changes and the local features. We than presents the formulas to compute the summary features : relative turn length and relative floor control.

\section{Local Features}

     We define a conversation as a sequence of dialogue acts $d_1 \dots d_N$, where $d_i$ is uttered by speaker $s_i$.  We write this as the following sequence:
%
     \begin{equation}
       \ldots  s_{i-2}, d_{i-2}, s_{i-1} , d_{i-1}, s_i, d_i  \ldots
     \end{equation}
     We denote whether there was a turn transition with $y_i$. A turn transition occurs when the speaker $s_i$ is different from speaker $s_{i-1}$. Hence, (1) can be also be viewed as a sequence of dialog acts $d_i$ followed by turn transitions $y_i$:
%
     \begin{equation}
       \ldots    d_{i-2}, y_{i-1}, d_{i-1}, y_{i} , d_i, y_{i+1} \ldots
     \end{equation}
      In our first baseline model, we try to predict the turn transition value $y_{i+1}$ based only on the latest dialog act $d_i$. In our second baseline model, we try to predict turn transition $y_{i+1}$ based on the latest two dialog acts: $d_{i-1}$ and $d_i$.


\section{Summary Features}\label{sfeatures}

     As discussed in the introduction, we introduce two types of summary features in this paper: relative turn length ($rt_i$) and relative floor control ($rc_i$).  These features are used in predicting whether there is a change in speaker $y_{i+1}$ after dialogue act $d_i$.

     To compute the summary features at dialogue act $d_i$, we introduced the some notation. Let $S_i$ to be the set of complete turns of speaker $s_i$ that are prior to the turn that $d_i$ is in.  Let $t_i$ represent the turn so far that $d_i$ is in, up to $d_i$ but no subsequent dialogue acts.  Let length(t) be the length of a turn or a partial turn in seconds (or words). To compute the \textit{relative turn length} of turn $t_i$ we first compute the average length of all the turns in $S_i$
%
    \begin{equation}
     avg\_t_i = \frac{\sum_{t \in S_i} length(t)}{|S_i|}
     \end{equation}
     The \textit{relative turn length} summary feature of $t_i$, denoted as $rt_i$, measures the percent of the length of the turn $t_i$ so far, relative to the average turn length up to $t_i$ of the current speaker $s_i$ (but not including $t_i$).
%
     \begin{equation}
            rt_i =  \frac{length(t_i)} {avg\_t_i}
     \end{equation}
     Note that we calculate two versions of $rt_i$: in seconds and in words.  The purpose of $rt_i$ is to let the listener, in predicting turn changes, take into account whether the current speaker is exceeding his or her average turn length.

     The \textit{relative floor control}, denoted as $rc_i$, measures the percent of time in which the current speaker controlled the conversation floor up to $d_i$. We use $S_i$ as defined above:
     the set of complete turns of speaker $s_i$ that are prior to the turn that $d_i$ is in.
     %
     We similarly define $L_i$ to be the turns of the other conversant (the listener of $d_i$) that are prior to $d_i$.
     %
     We first compute the conversation length up to $d_i$ denoted as $c_i$, which excludes inter-utterance pauses but includes intra-utterance pauses.
     \begin{equation}
         c_i = \sum_{t \in S_i \cup L_i} length(t)
     \end{equation}
     To compute relative floor control at $d_i$, we divide the floor time of the speaker $s_i$ up to turn $t_i$ by $c_i$:

     \begin{equation}
        rc_i = \frac{\sum_{t \in S_i} length(t)} {c_i}
     \end{equation}
     Note that we calculate $rc_i$ in seconds and in words. Participants can use the relative floor control as a means to determine if one speaker is controlling the conversation; a controlling speaker will probably be less inclined to give up the floor.

     We use these two summary features in the \textit{summary model} and \textit{full model}, as described in the next section.


