% Example thesis demonstrating cslu-thesis.cls usage
%
% Document options:
%
% copyright - include a copyright page
% listoftables - include a list of tables
% listoffigures - include a list of figures
% twoside - format for two-sided printing and binding
% masters - generate a Master's thesis instead of a Ph.D. thesis
%
% All other options are passed to the underlying report class, e.g., 10pt
\documentclass[copyright,masters]{cslu-thesis}

\usepackage{lipsum} % for placeholder content text only
\usepackage{tabularx}
\usepackage{graphicx}
\usepackage{amssymb,amsmath,bm}
\usepackage{textcomp}
\usepackage{tkz-graph}
\usepackage{enumitem}
\usepackage{listings}
\usepackage{booktabs}

\GraphInit[vstyle = Shade]
\tikzset{
  LabelStyle/.style = { rectangle, rounded corners, draw,
                        minimum width = 2em, fill = yellow!50,
                        text = red, font = \bfseries },
  VertexStyle/.append style = { inner sep=5pt,
                                font = \Large\bfseries},
  EdgeStyle/.append style = {->, bend left} }

\def\vec#1{\ensuremath{\bm{{#1}}}}
\def\mat#1{\vec{#1}}


\lstset{language=Java,
  showstringspaces=false,
  columns=flexible,
  basicstyle={\small\ttfamily},
  numbers=none,
  numberstyle=\tiny\color{gray},
  keywordstyle=\color{blue},
  commentstyle=\color{dkgreen},
  stringstyle=\color{mauve},
  breaklines=false,
  breakatwhitespace=false,
  tabsize=3
}

\begin{document}


% Required info for title page and elsewhere
\title{Using Past Speaker Behavior to Better Predict Turn Transitions}
\author{Tomer M.\ Meshorer}
\previousdegrees{B.\,A. Computer Science, Tel Aviv University, 1997}
\discipline{Computer Science \& Engineering}
% Advisor, readers are in {Name}{Title} format
% Fourth reader is optional; all others are required
\principaladvisor{Prof. Peter A. Heeman}{Research Associate Professor}
\firstreader{Steven Bedrick}{Research Assistant Professor}
\secondreader{Stephen Wu}{Research Associate Professor}
%\thirdreader{NA}{NA}
% Date degree will be conferred
\degreedate{March}{2017}
% Override the default department if needed
% Default is "Center for Spoken Language Understanding"
%\renewcommand{\department}{Department of Biomedical Engineering}


% Front matter
% Title, copyright, signature pages
% See document options above
\frontmatter


% Additional preface sections (optional)
\prefacesection{Dedication}
I would like to dedicate this work to my father, Israel Sagie $(1945-2016)$, who passed away during the preparation of this work.
His wisdom and support will always guide me.
\prefacesection{Acknowledgements}
I would like to express my deep appreciation to Prof. Peter Heeman for his guidance during this research. Without his valuable assistance,
I could not have completed this work.

I would also like to express my appreciation to the members of the committee, Prof. Steven Bedrick and Prof. Stephen Wu, for reviewing
the work and providing invaluable feedback.

I am also indebted to the staff and students of the Center of Spoken Language Understanding, and especially to the gradate program coordinator, Ms. Patricia Dickerson,
for her valuable assistance during the course of my studies.
This work was funded by the National Science Foundation under grant IIS-1321146.


% Table of contents, lists of tables/figures
% See document options above
\tableofcontents


% Abstract
\abstract
 Conversations are at the core of everyday social interactions. The interactions between conversants are preformed within the realm of a sophisticated and self-managed turn taking system. In human conversations, the turn taking system  supports minimal speaker overlap during turn transitions and minimum gaps between turns. Spoken dialogue systems are a new form of conversational user interface that permits users to use their voice to interact with the computer. As such, the turn taking capabilities of SDS should evolve from a simple timeout to a more human-like model. Recent advances in turn taking systems for SDS use different local features of the last few utterances to predict turn transition.

This thesis explores using a summary of past speaker behavior to better predict turn transitions. We believe that the summary features represent an evolving model of the other conversant. For example, speakers who typically use long turns will be likely to use long turns in the future. Moreover, speakers with more control of the conversation floor will be unlikely to yield their turn often. As the conversational image of the speaker evolves with the conversation, other speakers might adjust their turn taking behavior in response.

We computed two types of summary features that represent the current speaker's past turn-taking behavior: \textit{relative turn length} and \textit{relative floor control}. Relative turn length measures the current turn length so far (in time and words) relative to the speaker's average turn length. Relative floor control measures the speaker's control of the conversation floor (in time and words) relative to the total conversation length. The features are recomputed for each dialog act based on past turns of the speaker within the current conversation. Using the switchboard corpus, we trained two models to predict turn transitions: one with just local features (e.g., current speech act, previous speech act) and one that added the summary features. Our results shows that using the summary features improves turn transitions prediction.
 % Main body
\body


\part{Introduction} % parts are optional, just chapters are OK too

\chapter{Introduction}
\input{p1}
\section{Thesis Statement}
\input{p2}
\section{Approach}
\input{p3}
\section{Dissertation Structure}
\input{p4}
\section{Contribution}
\input{p5}
\chapter{Related Work}
\input{p6}
\section{Human-Human Conversations}
\input{p7}
\section{Human-Computer Conversations}
\input{p8}
\chapter{Long term features over all past turns}
\section{Data}
\input{p9}
\section{Data Preparation}
\input{p10}
\section{Data Exploration}
\input{visualization}
\section{Results}
\input{p11}
\chapter{Conclusions}
\input{p12}
\section{Future Direction}
\input{p14}


% Appendix
\appendix


% Bibliography
\nocite{*} % temporarily include all references, even if not cited
\bibliographystyle{abbrv} % check with your advisor for appropriate style
\bibliography{thesis} % name of your thesis.bib file


% Biographical note
%\biography
%\lipsum[9]


\end{document}
